Analysis paper

### 2021-06-08 analysis/analysis.Rmd
update plots

coverage_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_phase, coverage, classification, range)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

scores_tables <- eval_forecasts(
  filtered_data[grepl("2", target)], 
  summarise_by = c("model", "target_phase", "classification", "horizon"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)

tbl <- scores_tables %>%
  merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification"))

 tbl <- tbl[, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]

tables <- list()
table_dfs <- list()
targets <- unique(tbl$target_phase)

for (tar in targets) {
  tables[[tar]] <- make_score_table(tbl[target_phase == tar])
}

for (tar in targets) {
  table_dfs[[tar]] <- tbl[target_phase == tar, 
                          .("Model" = model, 
                            # "Target" = target_phase,
                            "WIS" = interval_score,
                            # "Rel. skill" = scaled_rel_skill, 
                            "Sharpn." = sharpness, 
                            "Underp.." = underprediction, 
                            "Overp." = overprediction)#, 
                            # "Bias" = bias,
                            # "50%-Cov." = `50`, 
                            # "90%-Cov." = `90`)
                          ]
}

# make plots with tables
library(gridExtra)

tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
             tableGrob(table_dfs[[2]]), 
             tableGrob(table_dfs[[3]]), 
             tableGrob(table_dfs[[4]]), 
             tableGrob(table_dfs[[5]]), 
             tableGrob(table_dfs[[6]]), 
             nrow = 2)

tbl_plt <- ggplotify::as.ggplot(tbl_plt)

tbl_plt

ggsave("plots/distribution_scores_table.png")

library(gt)

tbl[, 
    .("Model" = model, 
      "Target" = target_phase,
      "WIS" = interval_score,
      # "Rel. skill" = scaled_rel_skill, 
      "Sharpn." = sharpness, 
      "Underp.." = underprediction, 
      "Overp." = overprediction)#, 
    # "Bias" = bias,
    # "50%-Cov." = `50`, 
    # "90%-Cov." = `90`)
] %>%
  gt(rowname_col = "Model", 
     groupname_col = "Target")

@@

scores_target <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "target_type", "classification", "forecast_date")
)

@@

```{r, eval = TRUE}
scores_full <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
  compute_relative_skill = FALSE, 
  baseline = "Baseline"
)

@@

scores_target <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "target_type", "classification", "range", "quantile"), 
  compute_relative_skill = FALSE, 
  pit_plots = TRUE
)

>>>>

```{r fig.height=10, fig.width=15}
# 
# coverage_tables <- eval_forecasts(
#   filtered_data[grepl("2", target)], 
#   summarise_by = c("model", "target_phase", "classification", "range", "horizon"), 
#   compute_relative_skill = TRUE, 
#   baseline = "Baseline"
# )[range %in% c(50, 90), 
#                    .(model, target_phase, coverage, classification, range)] %>%
#   dcast(formula = ... ~ range, value.var = "coverage")
# 
# scores_tables <- eval_forecasts(
#   filtered_data[grepl("2", target)], 
#   summarise_by = c("model", "target_phase", "classification", "horizon"), 
#   compute_relative_skill = TRUE, 
#   baseline = "Baseline"
# )
# 
# tbl <- scores_tables %>%
#   merge(coverage_tables, all.x = TRUE, by = c("model", "target_phase", "classification")) 
# 
#  tbl <- tbl[, lapply(.SD, FUN = function(x) {
#     if (is.numeric(x)) {
#       return(round(signif(x, 3), 2))
#     } else {
#       return(x)
#     }
#   })]
# 
# tables <- list()
# table_dfs <- list()
# targets <- unique(tbl$target_phase)
# 
# for (tar in targets) {
#   tables[[tar]] <- make_score_table(tbl[target_phase == tar])
# }
# 
# for (tar in targets) {
#   table_dfs[[tar]] <- tbl[target_phase == tar, 
#                           .("Model" = model, 
#                             # "Target" = target_phase,
#                             "WIS" = interval_score,
#                             # "Rel. skill" = scaled_rel_skill, 
#                             "Sharpn." = sharpness, 
#                             "Underp.." = underprediction, 
#                             "Overp." = overprediction)#, 
#                             # "Bias" = bias,
#                             # "50%-Cov." = `50`, 
#                             # "90%-Cov." = `90`)
#                           ]
# }
# 
# 
# # make plots with tables
# library(gridExtra)
# 
# tbl_plt <- grid.arrange(tableGrob(table_dfs[[1]]), 
#              tableGrob(table_dfs[[2]]), 
#              tableGrob(table_dfs[[3]]), 
#              tableGrob(table_dfs[[4]]), 
#              tableGrob(table_dfs[[5]]), 
#              tableGrob(table_dfs[[6]]), 
#              nrow = 2) 
# 
# tbl_plt <- ggplotify::as.ggplot(tbl_plt)
# 
# tbl_plt
# 
# ggsave("plots/distribution_scores_table.png")
# 
# library(gt)
# 
# tbl[, 
#     .("Model" = model, 
#       "Target" = target_phase,
#       "WIS" = interval_score,
#       # "Rel. skill" = scaled_rel_skill, 
#       "Sharpn." = sharpness, 
#       "Underp.." = underprediction, 
#       "Overp." = overprediction)#, 
#     # "Bias" = bias,
#     # "50%-Cov." = `50`, 
#     # "90%-Cov." = `90`)
# ] %>%
#   gt(rowname_col = "Model", 
#      groupname_col = "Target") 
#

@@

scores_target <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "target_type", "classification", "forecast_date")
)

@@

```{r, eval = TRUE}
scores_full <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "location_target", "horizon", "forecast_date"), 
  compute_relative_skill = FALSE, 
  baseline = "Baseline"
)

@@

scores_target <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "target_type", "classification", "range", "quantile"), 
  compute_relative_skill = FALSE, 
  pit_plots = TRUE
)
